---
title: "Homework5"
format: html
editor: visual
---

We are going to read in the two datasets, titled, "mat" and "port"

```{r}
#math <- read.csv("student-mat.csv")
#port <- read.csv("student-por.csv")
```

```{r}
#library(DBI)
#library(dplyr)
#dplyr::inner_join(mat, port, by=is.not(G1, G2, G3, paid, absences))

```

Categorical Variables

**Contingency Tables:**

Create a one-way contingency table, a two-way contingency table, and a three-way contingency table.

```{r}
#conTable1 = table(school)
#print(conTable1)
```

Two-way contingency table

```{r}
#math <- math |>
  #mutate(famsize = as.character(famsize),
         #SexF = factor(Sex, levels = c("female", "male"), labels = c("Female", "Male"))
#app_data
```

Three-way contingency table

```{r}
#math <- math |>
  #mutate(famsize = as.character(famsize),
         #school = as.character(school),
         #SexF = factor(Sex, levels = c("female", "male"), labels = c("Female", "Male"))
#app_data
```

```{r}
#math <- math |>
  #mutate(famsize = as.character(famsize),
         #school = as.character(school),
         #SexF = factor(Sex, levels = c("female", "male"), labels = c("Female", "Male")),
         #MedU = as.numeric(medu)
#app_data
```

Create a conditional two-way table using **table()**

```{r}
#table(port$age, port$absences, port$G1, port$G2, port$G3)
```

Numeric variables (and across groups)
The numeric variables are age, absences, and the three test grades variables (G1, G2, and G3) from each
data set (math and Portuguese).

```{r}
#math |>
  #summarize(across(where(is.numeric), 
                   #list("mean" = mean, "median" = median), 
                   #.names = "{.fn}_{.col}"))

#port |>
  #summarize(across(where(is.numeric), 
                   #list("mean" = mean, "median" = median), 
                   #.names = "{.fn}_{.col}"))

#math |>
  #summarize(across(where(is.numeric), 
                   #list("mean" = ~ mean(.x, na.rm = TRUE), "median" = ~ median(.x, na.rm = TRUE)), 
                   #.names = "{.fn}_{.col}"))

#port |>
  #summarize(across(where(is.numeric), 
                   #list("mean" = ~ mean(.x, na.rm = TRUE), "median" = ~ median(.x, na.rm = TRUE)), 
                   #.names = "{.fn}_{.col}"))
```

```{r}
#cor(math, method = c("pearson", "kendall", "spearman"))
#cor(portuguese, method = c("pearson", "kendall", "spearman"))
```

```{r}
#install.packages("ggplot2")
# Load ggplot2
#library("ggplot2")
```

```{r}
#g <- ggplot(math |> drop_na(math$age), aes(x = math$age))
#g + geom_density()

#g01 <- ggplot(math |> drop_na(math$absences), aes(x = math$absences))
#g01 + geom_density()

#g02 <- ggplot(math |> drop_na(math$G1), aes(x = math$G1))
#g02 + geom_density()

#g03 <- ggplot(math |> drop_na(math$G2), aes(x = math$G2))
#g03 + geom_density()

#g04 <- ggplot(math |> drop_na(math$G3), aes(x = math$G3))
#g04 + geom_density()

#g1 <- ggplot(port |> drop_na(port$age), aes(x = port$age))
#g1 + geom_density()

#g2 <- ggplot(port |> drop_na(port$absences), aes(x = port$absences))
#g2 + geom_density()

#g3 <- ggplot(port |> drop_na(port$G1), aes(x = port$G1))
#g3 + geom_density()

#g4 <- ggplot(port |> drop_na(port$G2), aes(x = port$G2))
#g4 + geom_density()

#g5 <- ggplot(port |> drop_na(port$G3), aes(x = port$G3))
#g5 + geom_density()
```

```{r}
#gboxplot <- ggplot(app_data |> drop_na(math$age)
#gboxplot + geom_boxplot(aes(x = math$age, fill = Diagnosis))
```

```{r}
#gboxplot <- ggplot(math |> drop_na(math$age, math$G1)
#gboxplot + geom_boxplot(aes(x = math$age, y = math$G1, fill = Diagnosis))
```

```{r}
#gboxplot <- ggplot(port |> drop_na(port$age, port$G1)
#gboxplot + geom_boxplot(aes(x = port$age, y = port$G1, fill = Diagnosis))
```

```{r}
#gscatterplot <- ggplot(port |> drop_na(port$absences, port$G3, port$age))
      #aes(x = port$absences, y=port$g3, color=port$age)
```
